The shape of kelp: environmental influences on kelp morphology

### 2018-10-29 chapter_2.Rmd
Morphological methods for shallow collections added

>>>>

Between February 2017 and Novevember 2018, morphological measurements for _Ecklonia maxima_ individuals in shallow water (<1m) at 5 sites along the Western Cape coast of South Africa were collected. These sites represent a wave gradient moving south along the peninsula and into False Bay. The same morphometric measurements were taken as per the deeper _Ecklonia maxima_, and this allowed comparison between morphological characteristics between deep and shallow individuals.
